Incentivizing Exploration by Heterogeneous Users

### 2018-02-16 Discussion.tex
addressed some comments

\begin{itemize}
\item $i$ has been pulled at most%
\footnote{in fact: exactly, since the algorithm entered phase $s$}
$s-1$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s-1$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms'
attribute vectors, the probability of pulling arm $i$ is less than $1/s$. Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
  \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
be the probability that arm $i$ will be pulled
by the next (random) agent based on the current estimates. 
Then, the second criterion for payment-eligibility is that
$\PullProb{t}{i} < 1/s$.
\end{itemize}

@@

\begin{theorem}
The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by $O(\ARMNUM^2)$. 
\end{theorem}

\begin{proof}
The proof is exact the same as the proof for Lemma~\ref{rst:budget} except we now define $s_2 =\frac{2}{p}$. The rest of the proof remains the same.
\end{proof}

\begin{lemma}  \label{lem:NumP1}
The expected number of time steps in which
Algorithm~\ref{alg:basic-incentivizing}
makes any payment is at most 
\begin{align}
O\left(\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right). \nonumber 
\end{align}
\end{lemma}

\begin{proof}
The proof is exact the same as the proof for Lemma~\ref{lem:numP} except we now define $\EvenLaterPhase = \max(50, \frac{92.16 \sigma^4}{x^4}, \frac{2}{p})$.
\end{proof}

@@

\begin{itemize}
\item $i$ has been pulled at most%
\footnote{in fact: exactly, since the algorithm entered phase $s$}
$s-1$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s-1$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms'
attribute vectors, the probability of pulling arm $i$ is less than $1/\log(s+s_0)$. Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
  \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
be the probability that arm $i$ will be pulled
by the next (random) agent based on the current estimates. 
Then, the second criterion for payment-eligibility is that
$\PullProb{t}{i} < 1/\log(s+s_0)$.
\end{itemize}

@@

\begin{theorem}
The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by $O(\ARMNUM^2)$. 
\end{theorem}

\begin{proof}
The proof is exact the same as the proof for Lemma~\ref{rst:budget} except we no longer needs $s_2$. The rest of the proof remains the same.
\end{proof}

\begin{lemma}  \label{lem:NumP2}
The expected number of time steps in which
Algorithm~\ref{alg:basic-incentivizing}
makes any payment is at most 
\begin{align}
O\left(\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right). \nonumber 
\end{align}
\end{lemma}

\begin{proof}
The proof is exact the same as the proof for Lemma~\ref{lem:numP} except we now define $\EvenLaterPhase = \max(50, \frac{92.16 \sigma^4}{x^4})$ since $\frac{1}{\log(s+s_0)}\leq \frac{p}{2}$ is true for all $s$.
\end{proof}

\begin{theorem}
The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
\begin{align}
O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} +\frac{\ARMNUM^2 d\MAXR}{p}+\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{p}\right).  \nonumber
\end{align}
\end{theorem}

\begin{proof}
The proof of this Theorem is similar as Theorem~\ref{rst:regret}, except
\begin{itemize}
\item We can use Lemma~\ref{lem:NumP2} to bound the regret when we decide to incentivize;
\item The expected length of phase $s$ is bounded by $\ARMNUM \log(s+s_0)$;
\item With the same choice of $g(s)$, the regret in Equation~\ref{equ:small_regret_bound} can now be bounded by $160 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1)\log(T+s_0)=O(\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{p})$.
\end{itemize}
The rest of the proof remains the same.
\end{proof}

>>>>

\begin{itemize}
\item $i$ has been pulled at most%
\footnote{in fact: exactly, since the algorithm entered phase $s$}
$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms'
attribute vectors, the probability of pulling arm $i$ is less than $1/s$. Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
  \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
be the probability that arm $i$ will be pulled
by the next (random) agent based on the current estimates. 
Then, the second criterion for payment-eligibility is that
$\PullProb{t}{i} < 1/s$.
\end{itemize}

@@

\begin{theorem}
The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
\begin{align*}
O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{p^{5/2}} \right). 
\end{align*}
\end{theorem}

\begin{proof}
The proof is exact the same as the proof for Theorem~\ref{rst:budget} except we now define $h(\ell) := \max \left( \frac{2}{\MinProb},
\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
\right)$. The rest of the proof remains the same.
\end{proof}

\begin{lemma}  \label{lem:NumP1}
The expected number of time steps in which
Algorithm~\ref{alg:basic-incentivizing}
makes any payment is at most 
\begin{align}
O\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
  + \frac{\ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right). \nonumber 
\end{align}
\end{lemma}

\begin{proof}
The proof is exact the same as the proof for Lemma~\ref{lem:numP} except we now define $\EvenLaterPhase = \max (2, \frac{30 \sigma^3}{x^3}, \frac{2}{p})$.
\end{proof}

@@

\begin{itemize}
\item $i$ has been pulled at most%
\footnote{in fact: exactly, since the algorithm entered phase $s$}
$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms'
attribute vectors, the probability of pulling arm $i$ is less than $1/\log(s+s_0)$. Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
  \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
be the probability that arm $i$ will be pulled
by the next (random) agent based on the current estimates. 
Then, the second criterion for payment-eligibility is that
$\PullProb{t}{i} < 1/\log(s+s_0)$.
\end{itemize}

@@

\begin{theorem}
The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
\begin{align*}
O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{p^{5/2}} \right). 
\end{align*}
\end{theorem}

\begin{proof}
The proof is exact the same as the proof for Lemma~\ref{rst:budget} except we define $h(\ell) := 
\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}$. The rest of the proof remains the same.
\end{proof}

\begin{lemma}  \label{lem:NumP2}
The expected number of time steps in which
Algorithm~\ref{alg:basic-incentivizing}
makes any payment is at most 
\begin{align}
O\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
  + \frac{\ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right). \nonumber 
\end{align}
\end{lemma}

\begin{proof}
The proof is exact the same as the proof for Lemma~\ref{lem:numP} except we now define $\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3})$ since $\frac{1}{\log(s+s_0)}\leq \frac{p}{2}$ is true for all $s$.
\end{proof}

\begin{theorem}
The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
\begin{align}
O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} +\frac{\ARMNUM^2 d\MAXR}{p}+\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{p}\right).  \nonumber
\end{align}
\end{theorem}

\begin{proof}
The proof of this Theorem is similar as Theorem~\ref{rst:regret}, except
\begin{itemize}
\item We can use Lemma~\ref{lem:NumP2} to bound the regret when we decide to incentivize;
\item The expected length of phase $s$ is bounded by $\ARMNUM \log(s+s_0)$;
\item With the same choice of $g(s)$, the regret in Equation~\ref{equ:small_regret_bound} can now be bounded by $71.11 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1)\log(T+s_0)=O(\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{p})$.
\end{itemize}
The rest of the proof remains the same.
\end{proof}
